SST_patterns

### 2020-01-20 SST_patterns.Rmd
update
edit

  -Correlate the 1st pixel with the second pixel and the first pixel with the last pixel
  -Correlation of the number of frequencies at different distances at each site

@@

distance_corr <- Combined_frequency %>% 
  group_by(site) %>% 
  slope_calc()

>>>>

  -Correlate the 1st pixel with the second pixel and the first pixel with the last pixel
  -Correlation between satellite data and number of signals at the different distances from the coastline

@@

distance_corr <- Combined_frequency %>% 
  group_by(site) %>% 
  slope_calc()
```
